Harmful Anti-Foreign Sentiments based on Concern for Competition Should be Recognized and Addressed

### 2023-02-17 outputs/paper/paper.qmd
Add estimand

In studying the opinions of German males living in municipalities with excess male populations, they find that a portion of non-immigrant German men hold the belief that refugees pose a threat to their ability to pursue German women [@main_paper]. Their finding suggest that hate crimes increase where non-immigrant German men are disadvantaged in their local dating markets [@main_paper]. By using ecological evidence and originally curated survey data, the paper concludes that competition in dating and marriage markets where men outnumber women increase anti-refugee sentiments and violence [@main_paper].

>>>>

In studying the opinions of German males living in municipalities with excess male populations, they find that a portion of non-immigrant German men hold the belief that refugees pose a threat to their ability to pursue German women [@main_paper]. Their findings for the estimand of non-immigrant German men suggest that hate crimes increase where non-immigrant German men are disadvantaged in their local dating markets [@main_paper]. By using ecological evidence and originally curated survey data, the paper concludes that competition in dating and marriage markets where men outnumber women increase anti-refugee sentiments and violence [@main_paper].
